Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-28 arxiv-version/main.tex
Add auxilliary lemma

Before we state the theorems, recall that a polynomial of $d$ variables is a
function $p:\R^d \to \R$ of the form
$$
p(x) = p(x_1, x_2, \dots, x_d) = \sum_{i_1, i_2, \dots, i_d} c_{i_1, i_2, \dots, i_d} x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}
$$
where the sum ranges over a finite set of tuples $(i_1, i_2, \dots, i_d)$ of
non-negative integers and $c_{i_1, i_2, \dots, i_d}$ is a real coefficient. The
\emph{degree} of a polynomial $p$, denoted by $\deg(p)$, is the largest value of
$i_1 + i_2 + \dots + i_d$ for which the coefficient is non-zero. The \emph{norm
of a polynomial} $p$ is defined as
$$
\norm{p} = \sqrt{\sum_{i_1, i_2, \dots, i_d} \left(c_{i_1, i_2, \dots, i_d} \right)^2 } \; .
$$

@@

>>>>

Before we state the theorems, recall that a polynomial of $d$ variables is a
function $p:\R^d \to \R$ of the form
$$
p(x) = p(x_1, x_2, \dots, x_d) = \sum_{i_1, i_2, \dots, i_d} c_{i_1, i_2, \dots, i_d} x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}
$$
where the sum ranges over a finite set of tuples $(i_1, i_2, \dots, i_d)$ of
non-negative integers and $c_{i_1, i_2, \dots, i_d}$ is a real coefficient. The
\emph{degree} of a polynomial $p$, denoted by $\deg(p)$, is the largest value of
$i_1 + i_2 + \dots + i_d$ for which the coefficient is non-zero. The \emph{norm
of a polynomial} $p$ is defined as
$$
\norm{p} = \sqrt{\sum_{i_1, i_2, \dots, i_d} \left(c_{i_1, i_2, \dots, i_d} \right)^2 } \; .
$$
It is not hard to see that this indeed a norm, since we can interpret it as
a Euclidean norm of the vector of the coefficients of the polynomial.

@@

\begin{proposition}[Properties of the norm of polynomials]
\hspace{1cm} % Dummy space
\begin{enumerate}
\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and
let $p(x) = \prod_{i=1}^n p_i(x)$ be their product. Then, $\norm{p}^2 \le n^{\sum_{i=1}^n \deg(p_i)} \prod_{i=1}^n \norm{p_i}^2$.
\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) = (q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then, $\norm{\sum_{i=1}^n p_i}^2 \le n \sum_{i=1}^n \norm{p_i}^2$.
\end{enumerate}
\end{proposition}

\begin{proof}
TODO

The second part follows from the first part by setting $p_1 = p_2 = \dots p_n = q$.

To prove the third part we use generalized triangle inequality and
an inequality $(\sum_{i=1}^n a_i)^2 \le n \sum_{i=1}^n a_i^2$ valid
for any real numbers $a_1, a_2, \dots, a_n$. (The latter inequality follows from the inequality
between arithmetic mean and qudratic mean, $\frac{1}{n} \sum_{i=1}^n a_i \le \sqrt{\frac{1}{n} \sum_{i=1}^n a_i^2}$.)
We have
\begin{align*}
\norm{\sum_{i=1}^n p_i}^2 = \left( \norm{\sum_{i=1}^n p_i} \right)^2 \le \left(\sum_{i=1}^n \norm{p_i} \right)^2 \le n \sum_{i=1}^n \norm{p_i}^2 \; .
\end{align*}
\end{proof}
